Output Summary

### 2022-04-21 03-post-process/output-plots.Rmd
Update residual visuals: observation model quantile residuals

```{r plot-obs-resid-fn}

obs_resid_yrs = all_yrs[c(1,observable)]

# function to plot a residual time series for one pop/origin/LH_type/age combo
# returns a data frame with identifiers and across-year summary statistics
plot_obs_resid = function(resid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {

  # extract the year indices available
  y_ind = get_yr_index(colnames(resid_post))

  # calculate posterior across-year mean and sd for each posterior sample
  mn_post = apply(resid_post, 1, mean)
  sd_post = apply(resid_post, 1, sd)

  # calculate posterior summaries of residual time series
  resid = apply(resid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))

  # place residuals at correct place in a time series
  # ie., insert missing values
  empty = matrix(NA, nrow = 5, ncol = length(obs_resid_yrs))
  empty[,y_ind] = resid
  resid = empty[,observable]
  rownames(resid) = c("mean", "sd", "50%", "2.5%", "97.5%")
  empty_names = rep(NA, length(obs_resid_yrs))
  empty_names[y_ind] = colnames(resid_post)

  # calculate posterior mean(last half of years) - mean(first half of years)
  y_first = 1:round(length(observable)/2)
  y_last = (max(y_first) + 1):length(observable)
  i_first = as.character(na.omit(empty_names[y_first]))
  i_last = as.character(na.omit(empty_names[y_last]))
  mn_post_first = apply(resid_post[,i_first], 1, mean)
  mn_post_last = apply(resid_post[,i_last], 1, mean)
  first_last_mn_diff_post = mn_post_last - mn_post_first

  # blank plot with correct dimensions
  par(lend = "square")
  plot(resid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "")

  # draw x-axis: years
  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], resid["2.5%",], all_yrs[observable], resid["97.5%",], col = "red")
  points(resid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

@@

  # create output for building summary tables
  data.frame(param = resid_param,
             pop = ifelse(!is.null(pop), pop, NA),
             origin = ifelse(!is.null(origin), origin, NA),
             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
             age = ifelse(!is.null(age), age, NA),
             n_yrs = ncol(resid_post[,y_ind %in% observable]),
             year_mean_mean = mean(mn_post),
             year_mean_lwr = unname(quantile(mn_post, 0.025)),
             year_mean_upr = unname(quantile(mn_post, 0.975)),
             year_sd_mean = mean(sd_post),
             year_sd_lwr = unname(quantile(sd_post, 0.025)),
             year_sd_upr = unname(quantile(sd_post, 0.975)),
             diff_mean = mean(first_last_mn_diff_post), 
             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
  )
}

@@

```{r fall-trap-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lPa_obs_resid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-trap-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lMb_obs_resid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Spring Trap Count) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r adult-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lRa_obs_resid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "log(Total Adult Count) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r summer-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Pb_Ma_resid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r fall-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Pa_Ma_resid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r winter-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_resid("Lphi_obs_Pa_Ma_resid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
  }
})
oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Smolt $\rightarrow$ LGR (NOR)

```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("Lphi_obs_Mb_Ma_resid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Smolt $\rightarrow$ LGR (HOR)

```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_resid("Lphi_obs_Mb_Ma_resid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
  }
})
oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r hydro-surv-resid, fig.width = 7, fig.height = 4}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_resid("Lphi_obs_Ma_O0_resid[year,origin]", origin = o, main = origins[o]))
oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r bon-adult-surv-resid, fig.width = 7, fig.height = 4}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_resid("x_LGR_obs_resid[year,origin]", origin = o, main = origins[o]))
oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("x_carcass_spawned_obs_resid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r summer-length-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lL_Pb_obs_resid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Mean Summer Length) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-length-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_resid("lL_Mb_obs_resid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Mean Spring Length) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

weir_comp_resid_plots = function(j) {
  my_par(); par(mfrow = c(2,3))
  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_resid("x_Ra_obs_resid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
  do.call(rbind, tmp)
}
```

@@

```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_resid_plots(j_cat)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_resid_plots(j_los)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_resid_plots(j_ugr)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r carcass-comp-resid-plots-fn}
carcass_comp_resid_plots = function(j) {
  my_par(); par(mfrow = c(2,3))
  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_resid("x_Sa_prime_obs_resid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
  do.call(rbind, tmp)
}
```

@@

```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_resid_plots(j_cat)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_resid_plots(j_los)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_resid_plots(j_min)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_resid_plots(j_ugr)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r obs-error-table-prep}
# rename parameters to human-readable format
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_resid\\[year,LH_type,pop\\]", "Fall Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_resid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_resid\\[year,pop\\]", "Adult Return")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_resid\\[year,pop\\]", "Summer Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_resid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_resid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_resid\\[year,origin\\]", "LGR Smolt -> Ocean")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_resid\\[year,origin\\]", "BON Adults -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_resid\\[year,pop\\]", "Pre-spawn")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_resid\\[year,pop\\]", "Summer Parr")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_resid\\[year,pop\\]", "Spring Smolt")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_resid\\[year,age,pop\\]", "Weir")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_resid\\[year,age,pop\\]", "Carcass")

@@

# determine whether posterior of across-year quantities overlaps the target value
obs_error_ests$yr_mean_incl_zero = ifelse(obs_error_ests$year_mean_lwr <= 0 & obs_error_ests$year_mean_upr >= 0, TRUE, FALSE)
obs_error_ests$yr_sd_incl_one = ifelse(obs_error_ests$year_sd_lwr <= 1 & obs_error_ests$year_sd_upr >= 1, TRUE, FALSE)
obs_error_ests$diff_incl_zero = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)

# format the mean values to present in table
# round and make bold if target value not in interval
obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_zero, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_one, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_zero, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)

>>>>

```{r plot-obs-resid-fn}
obs_qresid_yrs = all_yrs[c(1,observable)]

# function to plot a residual time series for one pop/origin/LH_type/age combo
# returns a data frame with identifiers and across-year summary statistics
plot_obs_qresid = function(qresid_param, year = ".+", pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {

  # extract posterior samples of residual time series
  qresid_post = post_subset(post, sub_index(qresid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)

  # extract the year indices available
  y_ind = get_yr_index(colnames(qresid_post))

  # calculate posterior across-year mean and sd for each posterior sample
  mn_post = apply(qresid_post, 1, mean)
  sd_post = apply(qresid_post, 1, sd)

  # calculate posterior summaries of qresidual time series
  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))

  # place qresiduals at correct place in a time series
  # ie., insert missing values
  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
  empty[,y_ind] = qresid
  qresid = empty[,observable]
  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
  empty_names = rep(NA, length(obs_qresid_yrs))
  empty_names[y_ind] = colnames(qresid_post)

  # calculate posterior mean(last half of years) - mean(first half of years)
  y_first = 1:round(length(observable)/2)
  y_last = (max(y_first) + 1):length(observable)
  i_first = as.character(na.omit(empty_names[y_first]))
  i_last = as.character(na.omit(empty_names[y_last]))
  mn_post_first = apply(qresid_post[,i_first], 1, mean)
  mn_post_last = apply(qresid_post[,i_last], 1, mean)
  first_last_mn_diff_post = mn_post_last - mn_post_first

  # set the y-axis limits: leave room at top for legend
  ylim = c(0,1.3)

  # blank plot with correct dimensions
  par(lend = "square")
  plot(qresid["mean",] ~ all_yrs[observable], main = main,  type = "n", ylim = ylim, xlim = range(all_yrs[observable]), xaxt = "n", xlab = "", ylab = "",yaxt = "n")

  # draw x-axis: years
  at_x = seq(min(all_yrs[observable]), max(all_yrs[observable]), 4)
  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))
  axis(side = 2, at = seq(0, 1, 0.25), labels = TRUE)

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

  # draw reference line at 25%, 50%, and 75% quantiles
  abline(h = c(0.25, 0.5, 0.75), lty = 3, col = "grey", lwd = 2)

@@

  # draw legend that shows estimate summaries
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  rect(usr[1], 1, usr[2], usr[4], border = "black", col = "grey90")
  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.025, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)
  box()

  # create output for building summary tables
  data.frame(param = qresid_param,
             pop = ifelse(!is.null(pop), pop, NA),
             origin = ifelse(!is.null(origin), origin, NA),
             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
             age = ifelse(!is.null(age), age, NA),
             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
             year_mean_mean = mean(mn_post),
             year_mean_lwr = unname(quantile(mn_post, 0.025)),
             year_mean_upr = unname(quantile(mn_post, 0.975)),
             year_sd_mean = mean(sd_post),
             year_sd_lwr = unname(quantile(sd_post, 0.025)),
             year_sd_upr = unname(quantile(sd_post, 0.975)),
             diff_mean = mean(first_last_mn_diff_post), 
             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
  )
}

@@

```{r fall-trap-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lPa_obs_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Fall Parr Abundance) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-trap-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lMb_obs_qresid[year,LH_type,origin,pop]", LH_type = 2, origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Spring Trap Count) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r adult-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lRa_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "log(Total Adult Count) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r summer-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pb_Ma_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Summer Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r fall-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Fall Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r winter-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Pa_Ma_qresid[year,LH_type,pop]", LH_type = 2, pop = j, main = pops[j])
  }
})
oma_labels("Brood Year", "logit(Winter Tagging to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

#### Spring Smolt $\rightarrow$ LGR {.tabset .tabset-pills}

```{r spring-surv-resid-nor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 1, main = pops[j]))
oma_labels("Brood Year", "logit(NOR Smolt to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

```{r spring-surv-resid-hor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) {
  if (j == 3) {
    no_data_plot(main = pops[j])
  } else {
    plot_obs_qresid("Lphi_obs_Mb_Ma_qresid[year,LH_type,origin,pop]", LH_type = 2, pop = j, origin = 2, main = pops[j])
  }
})
oma_labels("Brood Year", "logit(HOR Smolt to LGR Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r hydro-surv-resid, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("Lphi_obs_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r bon-adult-surv-resid, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_obs_qresid("x_LGR_obs_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Return Year", "Count of PIT Tagged Adults at LGR Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r pre-spawn-surv-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("x_carcass_spawned_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "Count of Female Spawned-out Carcasses Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r summer-length-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Pb_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Mean Summer Length) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

```{r spring-length-resid, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_obs_qresid("lL_Mb_obs_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Mean Spring Length) Residual")
obs_error_ests = rbind(obs_error_ests, do.call(rbind, tmp))
```

@@

weir_comp_qresid_plots = function(j) {
  my_par(); par(mfrow = c(2,3))
  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Ra_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Ra[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
  oma_labels("Return Year", "Weir Age/Origin Composition Residual")
  do.call(rbind, tmp)
}
```

@@

```{r cat-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_qresid_plots(j_cat)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r los-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_qresid_plots(j_los)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r ugr-weir-comp-resids, fig.width = 8, fig.height = 5}
tmp = weir_comp_qresid_plots(j_ugr)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r carcass-comp-resid-plots-fn}
carcass_comp_qresid_plots = function(j) {
  my_par(); par(mfrow = c(2,3))
  tmp = lapply(1:jags_data$nko, function(ko) plot_obs_qresid("x_Sa_prime_obs_qresid[year,age,pop]", year = unname(which(jags_data$nx_Sa_prime[,j] > 0)), age = ko, main = ko_names[ko], pop = j))
  oma_labels("Return Year", "Carcass Age/Origin Composition Residual")
  do.call(rbind, tmp)
}
```

@@

```{r cat-carcass-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_qresid_plots(j_cat)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r los-carcas-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_qresid_plots(j_los)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r min-carcas-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_qresid_plots(j_min)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r ugr-carcass-comp-resids, fig.width = 8, fig.height = 5}
tmp = carcass_comp_qresid_plots(j_ugr)
obs_error_ests = rbind(obs_error_ests, tmp)
```

@@

```{r obs-error-table-prep}
# rename parameters to human-readable format
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lPa_obs_qresid\\[year,LH_type,pop\\]", "Fall Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lMb_obs_qresid\\[year,LH_type,origin,pop\\]", "Spring Screw Trap")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lRa_obs_qresid\\[year,pop\\]", "Adult Return")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pb_Ma_qresid\\[year,pop\\]", "Summer Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Pa_Ma_qresid\\[year,LH_type,pop\\]", "Fall Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Mb_Ma_qresid\\[year,LH_type,origin,pop\\]", "Spring Tagging -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "Lphi_obs_Ma_O0_qresid\\[year,origin\\]", "LGR Smolt -> Ocean")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_LGR_obs_qresid\\[year,origin\\]", "BON Adults -> LGR")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_carcass_spawned_obs_qresid\\[year,pop\\]", "Pre-spawn")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Pb_obs_qresid\\[year,pop\\]", "Summer Parr")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "lL_Mb_obs_qresid\\[year,pop\\]", "Spring Smolt")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Ra_obs_qresid\\[year,age,pop\\]", "Weir")
obs_error_ests$param = stringr::str_replace(obs_error_ests$param, "x_Sa_prime_obs_qresid\\[year,age,pop\\]", "Carcass")

@@

# determine whether posterior of across-year quantities overlaps the target value
obs_error_ests$yr_mean_incl_target = ifelse(obs_error_ests$year_mean_lwr <= 0.5 & obs_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
obs_error_ests$yr_sd_incl_target = ifelse(obs_error_ests$year_sd_lwr <= sqrt(1/12) & obs_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
obs_error_ests$diff_incl_target = ifelse(obs_error_ests$diff_lwr <= 0 & obs_error_ests$diff_upr >= 0, TRUE, FALSE)

# format the mean values to present in table
# round and make bold if target value not in interval
obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)
